\documentclass{Paper_Summary}

% ================================== VARIABLES ================================== 
\renewcommand{\varpapertitle}{{Age-Related Differences in Formal Thought Disorderin Chronically Hospitalized Schizophrenic Patients:A Cross-Sectional Study Across Nine Decades}}
\renewcommand{\varpaperauthor}{Harvey F, Leibman L, Al E.}
\renewcommand{\vardate}{{September 2021}}
% ================================== ========= ================================== 

\begin{document}
\makepapertitle

\breakline

\begin{center}
    \section*{Critique}
\end{center}
    
    Although an interesting paper there is not much to take away into my own work. I say this since:
    \begin{enumerate}
        \item It does not focus on identifying schizophrenia / thought disorder / psicosis from a control group but instead is trying to evaluate the progression of the disease throughout age.
        \item Focuses on diagnosis using medically recognized scales and diagnosis tools, which although possibly interesting for extrapolation of charactheristics will not be the objective. The objective is instead on using other factors in order support medical professionals on their diagnosis.
    \end{enumerate}

    Nontheless, there are some key points that can be taken from the paper that might be pertinent to my own work:
    \begin{enumerate}
        \item Good for understanding that mental illness can have a natural progression while aging and that some key aspects and charactheristics (evaluated through metrics) can change from age to age. → Bringing me to the conclusion that age should definitelly be a key aspect to evaluate in my work, maybe sepparate according to ages in groups and evalaute if some metrics are more noticible when discretized this way.
        \item Specific mention of important scales to reliably diagnosis thought disorders, which might lead to conclusions of which charactheristics are more proeminent to evaluate schizophrenia and consequently which metrics are better to evaluate this charactheristics.
        \item Mention of some analytical functions used to evaluate data (\href{https://en.wikipedia.org/wiki/Multivariate_analysis_of_variance}{MANOVA} and \href{https://en.wikipedia.org/wiki/Analysis_of_variance}{ANOVA}), although nothing out of the ordinary.
    \end{enumerate}

\breakline

\end{document}
