\documentclass{Paper_Summary}

% ================================== VARIABLES ================================== 
\renewcommand{\varpapertitle}{{Attenuated Frontal Activation During a Verbal Fluency Taskin Patients With Schizophrenia}}
\renewcommand{\varpaperauthor}{Curtis V, Bullmore E, Brammer M, et al.}
\renewcommand{\vardate}{{October 2021}}
% ================================== ========= ================================== 

\begin{document}
\makepapertitle

\breakline

\begin{center}
    \section*{Critique}
\end{center}
    
    Whereas some papers go too soft on the deeper meaning of schizophrenia psychosis and their analysis, this paper does not.
    The study analyzes MRI imaging of functioning brains during the execution of tasks and tries to compare patients with control.

    There are some problems with the study, such as:
    \begin{itemize}
        \item Small sample for test purposes. 
        \item There were patients under medication, which might have affected results. 
    \end{itemize}
    However, this is not relevant since the thesis will not be entering this level of detail.

    What is particularly interesting regarding this paper is that it proves that there are, or at least appear to be, some innate differences in the cerebral functions of controls and schizophrenic patients.
    
    These differences occurred even in covert experiments and in regions not typically associated with speech. Therefore, analyzing the context and discourse's meaning might reveal some interesting aspects regarding patients with schizophrenia.

\breakline

\end{document}
