\documentclass{Paper_Summary}

% ================================== VARIABLES ================================== 
\renewcommand{\varpapertitle}{{Graph analysis of dream reports is especially informative about psychosis}}
\renewcommand{\varpaperauthor}{Mota N. Furtado R. Maia P et al.}
\renewcommand{\vardate}{{October 2021}}
% ================================== ========= ================================== 

\begin{document}
\makepapertitle

\breakline

\begin{center}
    \section*{Critique}
\end{center}

    This study, by the same authors, that the previous studies, once again focus on \emph{Word Graphs} and their capability for an accurate and yet fast assessment of clinical state.

    There are some differences from the previously read experiments, which also used \emph{Word Graphs}:
    \begin{enumerate}
        \item Instead of focusing on the prediction of clinical state, the focus is on the correct \textbf{identification/differentiation} of different groups (schizophrenia disorder, bipolar disorder, and control group).
        \item The use of more \textbf{word graph attributes}, that although not proving to be needed, the authors used to assess possible relations.
        \item Evaluated the differences between \emph{dream and waking} reports in general and in each subgroup. By the end, the authors concluded on the best technique to identify the subject's clinical disorder.
    \end{enumerate}

    Interestingly enough, schizophrenic patients' discourse showed significantly fewer differences between \emph{dream and waking} reports than the remaining groups.

    The results obtained were maintained even after translating the transcripts into other five western languages, increasing the results obtained with the study.

    Once again, the thesis' work could follow the approach present on the paper during the \emph{affective pictures description} since this is the section of the test where the subject is freer to express itself and does not rely on readings and retellings or single disconnected words.

\breakline

\end{document}
